\boldmath Commissioning of the highly granular SiW-ECAL technological prototype

### 2019-04-04 performance-paper-draft/commissioning_arxiv1810.05133/arxiv-v1/draft_arxiv-v1.tex
Up to date to the arxiv submissions

\usepackage{jinstpub} % for details on the use of the package, please
                     % see the JINST-author-manual

@@

\author{\centering S.\,Bilokin\footnote{ Now at IPHC, Strasbourg.}, J.\,Bonis, P.\,Cornebise, A.\,Gallas, A.\,Irles,  R.\,P\"oschl, F.\,Richard, A.\,Thiebault, D.
\,Zerwas \\ {\it Laboratoire de l'Acc\'elerateur Lin\'eaire, CNRS/IN2P3 et Universit\'e de Paris-Sud XI, Centre Scientifique d'Orsay B\^atiment 200, BP 34, F-91898 Orsay 
CEDEX, France } 
\\ M.\,Anduze, V.\,Balagura, V.\,Boudry, J-C.\,Brient, E.\,Edy, G.\,Fayolle, M.\,Frotin, F.\,Gastaldi, A.\,Lobanov, F.\,Magniette, J.\,Nanni, M.\,Rubio-
Roy \footnote{ Now at Spintec, Grenoble} , K.\,Shpak, H.\,Videau, D.\,Yu\footnote{ Now at IHEP, Beijing.} \\ {\it Laboratoire Leprince-Ringuet (LLR) -- \'{E}cole Polytechnique, 
CNRS/IN2P3, Palaiseau, F-91128 France } 
\\ S.\,Callier, F.\,Dulucq, Ch.\,de la Taille, N.\,Seguin-Moreau \\ {\it Laboratoire OMEGA -- \'{E}cole Polytechnique-CNRS/
IN2P3, Palaiseau, F-91128 France } 
\\ J.E.\,Augustin, R.\,Cornat, J.\,David, P.\,Ghislain, D.\,Lacour, L.\,Lavergne\footnote{ Now at IRAP, Toulouse.}, J.M.\, Parraud \\ {\it Laboratoire de Physique Nucl\'eaire et de Hautes Energies 
(LPNHE), Sorbonne Universit\'e, UPD, CNRS/IN2P3, 4 Place Jussieu, 75005 Paris, France } 
\\ K.\,Kawagoe, Y.\,Miura, I.\,Sekiya, T.\,Suehara, T.\,Yoshioka, \\ {\it Department of Physics and Research Center for Advanced Particle Physics, 
 Kyushu University, 744 Motooka, Nishi-ku, Fukuoka 819-0395, Japan } 
\\ D.\,Jeans \\ {\it Institute of Particle and Nuclear Studies, KEK, 1-1 Oho, Tsukuba, Ibaraki 305-0801, Japan } 
\\ J.\,S.\,Chai \\ {\it Department of Electrical and Computer Engineering, Sungkyunkwan Universtity, 16419, Suwon, Gyeonggi-do, Korea}}

@@

\begin{figure}[!t]
  \centering
  \begin{tabular}{ll}
    \includegraphics[width=2.8in]{ped_mean_layer2-eps-converted-to.pdf} & \includegraphics[width=2.8in]{width_mean_layer2-eps-converted-to.pdf}
  \end{tabular}
  \caption{Pedestal mean position (left plot) and width (right plot) for all channels in one layer.}
\label{pedestal_layer}
\end{figure}

\begin{figure}[!t]
  \centering
  \begin{tabular}{ll}
    \includegraphics[width=2.8in]{h_ped_mean-eps-converted-to.pdf} & \includegraphics[width=2.8in]{h_ped_width-eps-converted-to.pdf}
  \end{tabular}
  \caption{Pedestal mean position (left) and width (right) for all channels and all SCAs in the setup.}
\label{pedestal_all}
\end{figure}

\begin{figure}[!t]
  \centering
  \begin{tabular}{ll}
      \includegraphics[width=2.8in]{MIPsummary_title-eps-converted-to.pdf} & \includegraphics[width=2.8in]{SNsummary_title-eps-converted-to.pdf}  
  \end{tabular}
\caption{Result of the MIP position calculation and signal over noise for the charge measurement on triggered channels for all calibrated channels.}
\label{mipandSN}
\end{figure}

@@

\begin{figure}[!t]
  \centering
  \begin{tabular}{ll}
    \includegraphics[width=2.8in]{summary_pedestal_chip12-eps-converted-to.pdf} & \includegraphics[width=2.8in]{summary_noise_chip12-eps-converted-to.pdf}
  \end{tabular}
  \caption{Average deviation of the pedestal mean position (left) and width (right) for all channels in the ASIC 12.}
\label{pedestal_magnetic}
\end{figure}

>>>>

%\usepackage{jinstpub} % for details on the use of the package, please
                     % see the JINST-author-manual
\usepackage{jinstpub} % for details on the use of the package, please

@@

\author{\centering S.\,Bilokin\footnote{ Now at IPHC, Strasbourg.}, J.\,Bonis, P.\,Cornebise, A.\,Gallas, A.\,Irles**,  R.\,P\"oschl, F.\,Richard, A.\,Thiebault, D.
\,Zerwas \\ {\it Laboratoire de l'Acc\'elerateur Lin\'eaire, CNRS/IN2P3 et Universit\'e de Paris-Sud XI, Centre Scientifique d'Orsay B\^atiment 200, BP 34, F-91898 Orsay 
CEDEX, France } 
\\ M.\,Anduze, V.\,Balagura, V.\,Boudry, J-C.\,Brient, E.\,Edy, G.\,Fayolle, M.\,Frotin, F.\,Gastaldi, A.\,Lobanov, F.\,Magniette, J.\,Nanni, M.\,Rubio-
Roy \footnote{ Now at Spintec, Grenoble} , K.\,Shpak, H.\,Videau, D.\,Yu\footnote{ Now at IHEP, Beijing.} \\ {\it Laboratoire Leprince-Ringuet (LLR) -- \'{E}cole Polytechnique, 
CNRS/IN2P3, Palaiseau, F-91128 France } 
\\ S.\,Callier, F.\,Dulucq, Ch.\,de la Taille, N.\,Seguin-Moreau \\ {\it Laboratoire OMEGA -- \'{E}cole Polytechnique-CNRS/
IN2P3, Palaiseau, F-91128 France } 
\\ J.E.\,Augustin, R.\,Cornat, J.\,David, P.\,Ghislain, D.\,Lacour, L.\,Lavergne\footnote{ Now at IRAP, Toulouse.}, J.M.\, Parraud \\ {\it Laboratoire de Physique Nucl\'eaire et de Hautes Energies 
(LPNHE), Sorbonne Universit\'e, UPD, CNRS/IN2P3, 4 Place Jussieu, 75005 Paris, France } 
\\ K.\,Kawagoe, Y.\,Miura, I.\,Sekiya, T.\,Suehara, T.\,Yoshioka, \\ {\it Department of Physics and Research Center for Advanced Particle Physics, 
 Kyushu University, 744 Motooka, Nishi-ku, Fukuoka 819-0395, Japan } 
\\ D.\,Jeans \\ {\it Institute of Particle and Nuclear Studies, KEK, 1-1 Oho, Tsukuba, Ibaraki 305-0801, Japan } 
\\ J.\,S.\,Chai \\ {\it Department of Electrical and Computer Engineering, Sungkyunkwan Universtity, 16419, Suwon, Gyeonggi-do, Korea}}

@@

\begin{figure}[!t]
  \centering
  \begin{tabular}{ll}
    \includegraphics[width=2.8in]{ped_mean_layer2-eps-converted-to.pdf} & \includegraphics[width=2.8in]{width_mean_layer2-eps-converted-to.pdf} 
  \end{tabular}
  \caption{Upper plots: pedestal mean position (left plot) and width (right plot) for all channels in one layer. Lower plots: same plots but after subtracting the corresponding averaged values calculated for each ASIC and SCA.}
\label{pedestal_layer}
\end{figure}

\begin{figure}[!t]
  \centering
  \begin{tabular}{ll}
    \includegraphics[width=2.8in]{h_ped_mean_notitle-eps-converted-to.pdf} & \includegraphics[width=2.8in]{h_ped_width_notitle-eps-converted-to.pdf} 
%%    \includegraphics[width=2.8in]{h_ped_mean_average-eps-converted-to.pdf} & \includegraphics[width=2.8in]{h_ped_width_average-eps-converted-to.pdf} \\
  \end{tabular}
  \caption{Pedestal mean position (left) and width (right) for all channels and all SCAs in the setup.}
\label{pedestal_all}
\end{figure}

\begin{figure}[!t]
  \centering
  \begin{tabular}{ll}
      \includegraphics[width=2.8in]{MIP_summary-eps-converted-to.pdf} & \includegraphics[width=2.8in]{SN_summary-eps-converted-to.pdf}  
  \end{tabular}
\caption{Result of the MIP position calculation and signal over noise for the charge measurement on triggered channels for all calibrated channels.}
\label{mipandSN}
\end{figure}

@@

\begin{figure}[!t]
  \centering
  \begin{tabular}{ll}
    \includegraphics[width=2.8in]{1T_summary_pedestal-eps-converted-to.pdf} & \includegraphics[width=2.8in]{1T_summary_noise-eps-converted-to.pdf}
  \end{tabular}
  \caption{Average deviation of the pedestal mean position (left) and width (right) for all channels in the ASIC 12.}
\label{pedestal_magnetic}
\end{figure}
